---
title: "Homework 4"
author: "Tyler Clay"
date: "3/29/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


Library

```{r}
library(readxl)
library(ggplot2)
library(rmarkdown)
library(ggpubr)
library(onewaytests)
library(car)
library(normtest)
library(moments)
library(dplyr)
library(dlookr)
library(gplots)
library(gtools)
library(gdata)
```



1) Fishies

Ho: The mean length of all fish is equal
Ha: The mean length of all fish is not equal

```{r}
#Assumptions of ANOVA
#Normal distribution
#Equal variance
#Random samples
#Independence
#Data is categorized in the same way

myfish<-read_excel('FishLength.xlsx')
#data<-as.numeric(unlist(mydata['length']))
str(myfish)
myfish$species<-as.factor(myfish$species)
str(myfish)

ggplot(myfish,aes(x=species))+
  geom_density(aes(group=length,color=length,fill=length),alpha=0.3)

levels(myfish$species)
group_by(myfish,species)
out.fish<-group_by(myfish,species)


```

Summary Stats

```{r}

#Normality was run here
normality(out.fish)

#Test for homogeneity of variances
bartlett.test(myfish$length~myfish$species)

```

ANOVA Test
```{r}

fish.test<-aov(length~species,data=myfish)
summary(fish.test)

```


Conclusion



2) T-Rex

Ho: The mean of all oxygen isotopes of all bones are equal
Ha: The mean of all oxygen isotopes of all bones are not equal 

```{r}

#Assumptions of ANOVA
#Normal distribution
#Equal variance
#Random samples
#Independence
#Data is categorized in the same way

myrex<-read_excel('t_rex.xlsx')
str(myrex)
myrex$bone<-as.factor(myrex$bone)
str(myrex)

levels(myrex$bone)
group_by(myrex,bone)
out.rex<-group_by(myrex,bone)

ggplot(myrex,aes(x=bone))+
  geom_density(aes(group=isotope_oxygen,color=isotope_oxygen,fill=isotope_oxygen),alpha=0.3)

```


Summary Stats

```{r}

#Normality was run here
normality(out.rex)

#Test for homogeneity of variances
bartlett.test(myfish$isotope_oxygen~myfish$bone)

```

ANOVA Test

```{r}

rex.test<-aov(isotope_oxygen~bone,data=myrex)
summary(rex.test)

```



Conclusion



3) Flies

Ho: The mean of the volume of flies is equal across all foliage types. 
Ha: The mean of the volume of flies is not equal across all foliage types.  

```{r}

###Assumptions of ANOVA
#Normal distribution
#Equal variance
#Random samples
#Independence
#Data is categorized in the same way

myfly<-read_excel('flies.xlsx')
str(myfly)
myfly$Foliage<-as.factor(myfly$Foliage)
str(myfly)

levels(myfly$Foliage)
group_by(myfly,Foliage)
fly.out<-group_by(myfly,Foliage)

ggplot(myfly,aes(x=Flies_m3))+
  geom_density(aes(group=Flies_m3,color=Flies_m3,fill=Flies_m3),alpha=0.3)

```


Summary Stats

```{r}

#Normality was run here
normality(fly.out)

#Test for homogeneity of variances
bartlett.test(myfly$Flies_m3~myfly$Foliage)

```

ANOVA Test

```{r}

fly.test<-aov(Flies_m3~Foliage,data=myfly)
summary(fly.test)

```


Conclusion



